%-------------------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    \textbf{\Huge \scshape Minjing Lee} \\ \vspace{1pt}
    \small +086-21-15921901226 $|$ \href{mailto:minjing.lee@sjtu.edu.cn}{\underline{minjing.lee@sjtu.edu.cn}} $|$ 
    \href{https://minjinglee.github.io}{\underline{Personal Website}}
\end{center}

\section{Research Interest}
{My research interest is in Analog and RF integrated circuits design. Currently I am interested in the tunable RF front-end circuits exploiting N-Path techniques. I hope to contribute to efficient and green integrated circuits and communication systems to improve the quality of life and help protect the beautiful earth I love.}
%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Shanghai Jiao Tong University}{Shanghai, China}
      {B.Eng in Microelectronics, minor in Philosophy}{Sep 2019 - June 2023(Expected)}
          \resumeItemListStart
            \resumeItem{\textbf{GPA: 90.15/100, 3.87/4.3 }(Ranked 4 out of 68 students)}
        \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------Research EXPERIENCE-----------
\section{Research Experience}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {RF Front-End Circuits exploiting N-Path Filters with 3x Passive Gain}{July 2022 – Present}
      {Center for Analog/RF Integrated Circuits(CARFIC), Shanghai Jiaotong University}{Shanghai, China}
      \resumeItemListStart
        \resumeItem{\textbf{Advisor:} Prof Xiaoming Liu and Prof Jing Jin}
        \resumeItem{Developed an N-Path Filter with 3x Passive Gain.}
        \resumeItem{Proposed a passive LNA by cascoding 3x Gain N-Path Filters to replace the conventional transformer, thus occupying less chip area than prior arts. \textbf{To be taped out with 55nm CMOS Technology and measured.}}
        \resumeItem{Proposed a gain-boosted high order N-Path filter.}
      \resumeItemListEnd
    \resumeSubheading
      {Low Power Successive Approximation Register Analog-to-Digital Converter}{Mar 2021 – Aug 2021}
      {Center for Analog/RF Integrated Circuits(CARFIC), Shanghai Jiaotong University}{Shanghai, China}
      \resumeItemListStart
        \resumeItem{\textbf{Advisor:} Prof Jing Jin}
        \resumeItem{Researched on calibration techniques for SAR ADC and dynamic amplifier design for pipelined SAR ADC.}
      \resumeItemListEnd  
     
    \resumeSubHeadingListEnd



%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart
     \resumeProjectHeading
          {\textbf{A Spice Circuit Simulator} $|$ \emph{MR325 Introduction to Design Automation}}{Sep 2022 -- Present}
         
      \resumeProjectHeading
          {\textbf{A Wideband Blocker-Tolerant Receiver} $|$ \emph{Center for Analog/RF Integrated Circuits}}{Mar 2022 -- Aug 2022}
          
         \resumeItemListStart
            \resumeItem{Implemented a 0.5-2GHz 4-path mixer-first receiver with 2nd order baseband TIA in 65nm CMOS Technology.}
            \resumeItem{Completed systematic tape-out flow including schematic design, simulation, layout and post-layout verification.}
            \resumeItem{Won \textbf{1st Prize} in National Final at the 6th China College IC Competition(IEEE Cup).}
            
         \resumeItemListEnd

      
         

    \resumeSubHeadingListEnd


%
\section{Awards \& Honors}

    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{National First Prize}{, The 6th China College IC Competition(IEEE Cup)}}{2022}
      
      \resumeProjectHeading
          {\textbf{Undergraduate Excellence Scholarship}{, Shanghai Jiao Tong University}}{2021}
      \resumeProjectHeading
          {\textbf{Taiwanese Student Scholarship}{, Shanghai Jiao Tong University}}{2019, 2020, 2021}

    \resumeSubHeadingListEnd
%-----------COMMUNITY AND LEADERSHIP-----------
\section{Community \& Leadership}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Outdoor Association, SJTU}{Dec 2021 – Present}
      {President}{}
%      \resumeItemListStart
%        \resumeItem{Job description/Award/Achievement 1}
%      \resumeItemListEnd
      
     \resumeSubheading
      {Philosophy Club, SJTU}{2021}
      {Co-Founder}{}

    \resumeSubheading
      {Baseball Team, SJTU}{Sep 2020 – Present}
      {Member}{}

    \resumeSubHeadingListEnd
%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Mandarin(Native), English} \\
     \textbf{Programming}{: C++, C, Verilog, Spice} \\
     \textbf{EDA Tools}{: Cadence Virtuoso, Cadence ADE}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
